A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-19 tex/body.tex
more

Not all normal interpretations are actually models of codatatypes, because
models must contain all possible infinite terms, not only cyclic ones. However,
only cyclic terms are interesting to us, and by monotonicity of ground
constraints it is trivial to extend a normal interpretation to an actual model.
Hence, we focus on normal interpretations.

>>>>

Not all normal interpretations are models of codatatypes, because
models must contain all possible infinite terms, not only cyclic ones. However,
only cyclic terms are interesting to us, and by monotonicity of ground
constraints it is trivial to extend any normal interpretation with additional
values. Hence, we focus on normal interpretations.
